---
title: Reproducibility - Preserving Survey Data
author:
  - Laurel Krovetz
  - Lars Vilhuber
date: January 2026
---

```{r config,include=FALSE}
library(readr)
library(here)
library(knitr)
library(dplyr)
library(ggplot2)
library(qualtRics)
library(lubridate)
library(qrcode)

# Qualtrics secrets are read from the environment:
# - QUALTRICS_API_KEY
# - QUALTRICS_BASE_URL

# We also need DATAVERSE secrets
#      DATAVERSE_TOKEN: ${{secrets.DATAVERSE_TOKEN}}
#      DATAVERSE_SERVER: https://demo.dataverse.org
#      DATAVERSE_DATASET_DOI: do
# Let's check that they are there:

message(Sys.getenv("QUALTRICS_BASE_URL"))

# The repository name

message(Sys.getenv("GITHUB_REPOSITORY"))

# Process the repository name to generate the URL
# - split the two components
# - combine them into a URL with 'github.io' in the middle

GITHUB_REPOSITORY <- Sys.getenv("GITHUB_REPOSITORY")
GITHUB_REPOSITORY_PARTS <- strsplit(GITHUB_REPOSITORY, "/")[[1]]
REPOSITORY_URL <- paste0("https://github.com/", GITHUB_REPOSITORY)
WEBSITE_URL <- paste0("https://", GITHUB_REPOSITORY_PARTS[1], ".github.io/", GITHUB_REPOSITORY_PARTS[2])

# qualtRics data:
# you can find this with all_surveys() %>% arrange(creationDate) %>% head()

QUALTRICS_FULL_URL <- "https://cornell.yul1.qualtrics.com/jfe/form"

# Public Qualtrics URL

QUALTRICS_SURVEY <- "SV_8Bbgqex21KyYDFY"

QUALTRICS_URL <- file.path(QUALTRICS_FULL_URL, QUALTRICS_SURVEY)

# Time when this was posted (discard anything before that)

QUALTRICS_STIME <- ymd_hms("2025-10-01 00:00:01")
QUALTRICS_ETIME <- ymd_hms("2026-01-14 23:59:00")


if (!dir.exists(here::here("data"))) {
  dir.create(here::here("data"))
}
```

::: {.panel-tabset}

## Introduction

Here we will demonstrate how to preserve raw survey data and also how to handle confidential data. We will do so with data from a  survey that you all will provide responses to. Some of the questions are meant to elicit "confidential" information from you as responses. You should not give your actual confidential information in response to these questions. We will use these questions as way to teach how to preserve data when some data are confidential. 


## Survey 

Please fill out this  survey:

<`r file.path(QUALTRICS_FULL_URL,QUALTRICS_SURVEY)`>



```{r, child=c(here::here('presentation','00-qrcode.md'))}
```

## Results

These are the results from all responses ever submitted. This might differ from the  [presentation](`r WEBSITE_URL`/presentation/)!

```{r downloaddata,include=FALSE}
# download data to local location

# if the Qualtrics API key is not set, we can't fetch the data
if (Sys.getenv("QUALTRICS_API_KEY") != "") {
  data.raw <- fetch_survey(surveyID = QUALTRICS_SURVEY, verbose = TRUE) 
  data <- data.raw |>
          filter(consent == "Yes") |>
          filter(Status != "Survey Preview") |>
          filter(StartDate > QUALTRICS_STIME & EndDate < QUALTRICS_ETIME) |>
    # renaming variables
    select(StartDate,EndDate,Status,Finished,RecordedDate,ResponseId,consent,age_1,gender,education,num_tabs_1,name_confidential,number_confidential)
} else {
  data <- data.frame()
}

```

```{r gender_table, results='asis', include=TRUE,echo=FALSE,message=FALSE}

if ( nrow(data) >0 ) {
data |>
  select(gender) |>
  group_by(gender) |>
  summarise(Frequency=n()) |>
  ungroup() |>
  mutate(Percent = round(Frequency/nrow(data)*100,2)) -> data.table

data.table |> kable()
} else {
  cat("No data yet. Check back later.")
}
```

```{r education_table, results='asis', include=TRUE,echo=FALSE,message=FALSE}
if ( nrow(data) >0 ) {
data |>
  select(education) |>
  group_by(education) |>
  summarise(Frequency=n()) |>
  ungroup() |>
  mutate(Percent = round(Frequency/nrow(data)*100,2)) -> data.table

data.table |> kable()
} else {
  cat("No data yet. Check back later.")
}
```

```{r age_table, results='asis', echo=FALSE, message=FALSE}
if (nrow(data) > 0) {
  cat("### Age")
  var_data <- data$age_1
  summary_stats <- data.frame(
    Statistic = c("Count", "Mean", "Median", "Min", "Max", "Std. Dev."),
    Value = c(
      sum(!is.na(var_data)),
      mean(var_data, na.rm = TRUE),
      median(var_data, na.rm = TRUE),
      min(var_data, na.rm = TRUE),
      max(var_data, na.rm = TRUE),
      sd(var_data, na.rm = TRUE)
    )
  )
  print(knitr::kable(summary_stats, digits = 2))
} else {
  cat("No data yet. Check back later.")
}
```

```{r tabs_table, results='asis', echo=FALSE, message=FALSE}
if (nrow(data) > 0) {
  cat("### Number of tabs open")
  var_data <- data$num_tabs_1
  summary_stats <- data.frame(
    Statistic = c("Count", "Mean", "Median", "Min", "Max", "Std. Dev."),
    Value = c(
      sum(!is.na(var_data)),
      mean(var_data, na.rm = TRUE),
      median(var_data, na.rm = TRUE),
      min(var_data, na.rm = TRUE),
      max(var_data, na.rm = TRUE),
      sd(var_data, na.rm = TRUE)
    )
  )
  print(knitr::kable(summary_stats, digits = 2))
} else {
  cat("No data yet. Check back later.")
}
```

## Why

For more information and steps on how to start creating a survey in Qualtrics, how to process and clean the data to remove confidential data, see this [presentation](`r WEBSITE_URL`/presentation/).



```{r, child=c(here::here('99-links.md'))}
```

## Log


```{r preserve data, include=TRUE,echo=TRUE,message=TRUE}
# Now save the data to a local file
if (nrow(data) > 0) {
  write_csv(data, here::here("data", "tutorial-survey.csv"))
  saveRDS(data, here::here("data", "tutorial-survey.rds"))
} else {
  # message("No data to save.")
}
```

:::